---
title: "Subsequent Infections - Figure S4 & S5"
date: "`r format(Sys.time(), '%m-%d-%y')`"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_collapsed: yes
    toc_float: yes
---

Report for progress on study modeling and analysis for the comparison of the presence of post-acute RSV infection in COVID-positive patients compared to comparison groups (influenza and other acute respiratory infections).

```{r setup, include=FALSE}
# Default taken from R notebook behavior: when knitting, wd will always be location of notebook
base_dir <- '..'
Sys.setenv(PEDSNET_SKIP_REQUEST_EXECUTION=1)
try(source('../site/run.R')) # May not be able to make db connection
#try(source('site/run.R'))

# Set to "local" to read data from ../results, or another value to read from db
data_source <- if_else(config('execution_mode') == 'distribution', 'local', 'not_local')

require(tibble)
require(knitr)
require(kableExtra)
require(readr)
require(table1)
require(ggplot2)
library(GGally)
require(tidyverse)
require(lubridate)
library(wesanderson)
library(survey)
library(survival)
library(WeightIt)
library(cobalt)
library(jtools)
require(cobalt)
require(WeightIt)
require(scattermore)
require(broom)
require(broom.mixed)
require(tableone)

get_results <- function(tbl_name) {
  if (data_source == 'local') {
    rslt <- read_csv(paste0('../results/', tbl_name, '.csv'))
  }
  else {
    rslt <- results_tbl(tbl_name) %>% collect()
  }
  rslt
}


prettify_kable <- function(data, indents = list()) {
  
  if (length(indents)==0) {
    data %>% 
      kbl(digits = 2, format.args = list(big.mark = ',')) %>%
      kable_classic(full_width = F, html_font = "Arial") %>% 
      kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>% 
      column_spec(1, bold = F, border_right = T)
  } else {
    data %>% 
      kbl(digits = 2, format.args = list(big.mark = ',')) %>%
      kable_classic(full_width = F, html_font = "Arial") %>% 
      kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>% 
      add_indent(indents) %>% 
      column_spec(1, bold = F, border_right = T)
  }
  
  # 
  # data %>% 
  #   kable(digits = 2, format.args = list(big.mark = ',')) %>% 
  #   kable_styling(bootstrap_options = c("striped", "hover")) %>% 
  #   column_spec(1, bold = T, border_right = T)
}

my.render.cont <- function(x) {
  with(stats.apply.rounding(stats.default(x), digits = 6), c("",
                                                             "Mean (SD)" = sprintf("%0.1f (%0.1f)", as.numeric(MEAN), as.numeric(SD)),
                                                             "Median [Q1-Q3]" = sprintf("%0.1f [%0.1f - %0.1f]", as.numeric(MEDIAN), as.numeric(Q1), as.numeric(Q3))
  ))
}

my.render.cat <- function(x) {
  c("", sapply(stats.default(x), function(y) {
    with(
      y,
      sprintf("%s (%0.1f%%)", format(FREQ, big.mark = ","), PCT)
    )
  }))
}

pvalue <- function(x, ...) {
  # Construct vectors of data y, and groups (strata) g
  # from https://cran.r-project.org/web/packages/table1/vignettes/table1-examples.html#example-a-column-of-p-values
  
  y <- unlist(x)
  g <- factor(rep(1:length(x), times = sapply(x, length)))
  if (is.numeric(y)) {
    # For numeric variables, perform a standard 2-sample t-test
    p <- t.test(y ~ g)$p.value
  } else {
    # For categorical variables, perform a chi-squared test of independence
    p <- chisq.test(table(y, g))$p.value
  }
  # Format the p-value, using an HTML entity for the less-than sign.
  # The initial empty string places the output on the line below the variable label.
  c("", sub("<", "&lt;", format.pval(p, digits = 3, eps = 0.001)))
}

# fron https://rdrr.io/github/junkka/ehahelper/src/R/broom_coxme.R
tidy.coxme <- function(x, exponentiate = FALSE, conf.int = 0.95, ...) {
  beta <- x$coefficients
  nvar <- length(beta)
  nfrail <- nrow(x$var) - nvar
  nn <- c("estimate", "exp()", "std.error", "statistic", "p.value")
  se <- sqrt(diag(as.matrix(x$var))[nfrail + 1:nvar])
  z <- qnorm((1 + conf.int) / 2, 0, 1)
  ret <- data.frame(
    "term" = names(beta),
    "estimate" = beta,
    "std.error" = se,
    "statistic" = beta / se,
    "p.value" = 1 - pchisq((beta / se)^2, 1),
    "conf.low" = beta - z * se,
    "conf.high" = beta + z * se,
    "beta" = beta
  )
  if (exponentiate) {
    ret$estimate <- exp(ret$estimate)
    ret$conf.low <- exp(ret$conf.low)
    ret$conf.high <- exp(ret$conf.high)
  }
  rownames(ret) <- c(1:nrow(ret))
  ret
}
```

# Data RSV

```{r data_RSV, include = FALSE, echo=FALSE, message=FALSE, warning=FALSE}
postacute_min_start_date = as.Date("2022-04-01")
postacute_max_end_date = as.Date("2023-01-01")

cohort_entry_start_date = as.Date("2022-03-01")
cohort_entry_end_date = as.Date("2022-07-01")

cohort_1_label = "rsv_study_cohort"

comparison_group_string = "Influenza"


analytic_dataset <-
  results_tbl(paste0(cohort_1_label, "_analytic_dataset_highrisk")) %>% 
  filter(ce_date >= cohort_entry_start_date,
         ce_date < cohort_entry_end_date)

analytic_dataset_final <-
  analytic_dataset %>% 
  filter(sex_cat != "Other/unknown") %>% 
  filter(is.na(covid_index_date_imputed) | covid_index_date_imputed==0) %>% 
  group_by(person_id) %>% 
  mutate(exclude = max(exclude_for_prior_rsv)) %>% 
  filter(exclude < 1) %>%
  slice_min(rsv_evidence_date, with_ties=FALSE) %>% 
  ungroup() %>% 
  mutate(lab_confirmed_index = ifelse(lab_confirmed==1, "lab confirmed", "dx only")) %>% 
  mutate(lab_confirmed_rsv_outcome = ifelse(lab_confirmed_rsv==1, "lab confirmed RSV", "dx only")) %>% 
  # mutate(visit_span_criteria_rank = as.character(visit_span_criteria_rank)) %>% 
  mutate(hospitalized_at_index = ifelse(hospital_flag==1 & visit_span_criteria_rank=="1", "Hospitalized", "Not hospitalized")) %>% 
  mutate(hospital_flag = as.character(hospital_flag)) %>% 
  mutate(hosp_with_vent = as.character(hosp_with_vent)) %>% 
  mutate(hospitalized_at_index = ifelse(is.na(hospitalized_at_index), "Not hospitalized", hospitalized_at_index)) %>% 
  mutate(hosp_with_vent = ifelse(is.na(hosp_with_vent), "0", hosp_with_vent))  %>% 
  mutate(hospitalized_at_index_detail = ifelse(hospitalized_at_index=="Hospitalized" & hosp_with_vent=="1", "Hospitalized with ventilation", hospitalized_at_index)) %>% collect() %>%
  mutate(pulmonary_respiratory = as.factor(pulmonary_respiratory),
         highrisk_flag = if_else(highrisk_flag, "Yes", "No"))


visit_counts <- results_tbl(paste0(cohort_1_label, "_visit_lookback_counts")) %>% 
  collect()

```

# Data Resp

```{r data_resp, echo = FALSE, output = FALSE, message = FALSE , warning = FALSE}
postacute_min_start_date_resp = as.Date("2021-07-01")
postacute_max_end_date_resp = as.Date("2023-03-01")

cohort_entry_start_date_resp = as.Date("2021-06-01")
cohort_entry_end_date_resp = as.Date("2023-01-01")
cohort_entry_end_date_resp = as.Date("2022-10-01")

cohort_1_label_resp = "resp_study_cohort"


# description = "covid_flu_3"
# description = "covid_flu_noutil"
# description = "covid_flu_util"
# description = "covid_ari_util"
# description = "covid_ari_ce_week"
# description = "covid_flu_nonexclude"

description_resp = "covid_flu_comparison"
# description = "covid_ari_comparison"
# comparison_group_string = "Respiratory"
comparison_group_string_resp = "Influenza"


analytic_dataset_resp <-
  results_tbl(paste0(cohort_1_label_resp, "_analytic_dataset_highrisk")) %>% 
  filter(ce_date >= cohort_entry_start_date_resp,
         ce_date < cohort_entry_end_date_resp)

analytic_dataset_final_resp <-
  analytic_dataset_resp %>% 
  filter(sex_cat != "Other/unknown") %>% 
  filter(is.na(covid_index_date_imputed) | covid_index_date_imputed==0) %>% 
  group_by(person_id) %>% # TODO might need to filter earliest resp date or something
  ungroup() %>% 
  mutate(lab_confirmed_index = ifelse(lab_confirmed==1, "lab confirmed", "dx only")) %>% 
  # mutate(visit_span_criteria_rank = as.character(visit_span_criteria_rank)) %>% 
  mutate(hospitalized_at_index = if_else(hospital_flag==1 & visit_span_criteria_rank=="1", "Yes","No")) %>% 
  mutate(hospital_flag = as.character(hospital_flag)) %>% 
  mutate(hosp_with_vent = as.character(hosp_with_vent)) %>% 
  mutate(hospitalized_at_index = if_else(is.na(hospitalized_at_index), "No", hospitalized_at_index)) %>% 
  mutate(hosp_with_vent = ifelse(is.na(hosp_with_vent), "0", hosp_with_vent))  %>% 
  mutate(hospitalized_at_index_detail = ifelse(hospitalized_at_index== "Yes" & hosp_with_vent=="1", "Hospitalized with ventilation", hospitalized_at_index)) %>% 
  mutate(resp_outcome_is_reinfection = case_when(resp_outcome_flu_related=="x" & sub_cohort=="Influenza" ~ "1",
                                                 outcome_covid30d=="1" & sub_cohort=="COVID" ~ "1",
                                                 TRUE ~ "0")) %>% 
  mutate(highrisk_flag = if_else(highrisk_flag, "Yes", "No")) %>%
  # mutate(rsv_outcome_postacute = ifelse(rsv_occurrence_period == "post acute (15-180 days after index)", 1, 0)) %>% 
  collect()

visit_counts_resp <- results_tbl(paste0(cohort_1_label_resp, "_visit_lookback_counts")) %>%
  collect()

```

# Figure S4a: RSV within 15-300 days (past post-acute)
```{r figs4a_rsv_15_300, echo = FALSE, output = FALSE, message = FALSE , warning = FALSE}

outcome_15_300 = "outcome_rsv_15_to_300"
comparison_group = "Influenza"
formula_no_pulmonary = "~ covid+ age_group + race_eth_cat + sex_cat + hospitalized_at_index +  util_inpatient +  util_outpatient +  util_ed + util_other"

# iptw_flu_15_300 <- analytic_dataset_final %>%
#   mutate(exclude = case_when( is.na(days_from_index_to_rsv) ~ 0,
#                               days_from_index_to_rsv >= 15 ~ 0,
#                               TRUE ~ 1)) %>%
#   filter(exclude==0) %>%
#   do_iptw(cohort_entry_start_date = cohort_entry_start_date,
#           comparison_cohort = comparison_group,
#           weight_formula = "covid~age_group+sex_cat+race_eth_cat+ce_week_factor",
#           iptw_description = paste0("covid_", comparison_group, "_", outcome_15_300))

rsv_iptw_15_300 <- results_tbl( paste0(paste0("covid_", comparison_group, "_", outcome_15_300),'_tabc')) %>% collect()
models_rsv_15_300 = list()

models_rsv_15_300$model_unweighted_unadjusted <- run_logistic_regression(df = rsv_iptw_15_300,
                                                                         model_formula = paste0(outcome_15_300, " ~ covid"),
                                                                         weight_method = "none")

models_rsv_15_300$model_unweighted_adjusted <- run_logistic_regression(df = rsv_iptw_15_300,
                                                                       model_formula = paste0(outcome_15_300,
                                                                                              formula_no_pulmonary), #, " + `Pulmonary Respiratory: `"), 
                                                                       weight_method = "none")

models_rsv_15_300$model_weighted_unadjusted <- run_logistic_regression(df = rsv_iptw_15_300,
                                                                       model_formula = paste0(outcome_15_300, " ~ covid"),
                                                                       weight_method = "lr")

models_rsv_15_300$model_weighted_adjusted <- run_logistic_regression(df = rsv_iptw_15_300,
                                                                     model_formula = paste0(outcome_15_300,
                                                                                            formula_no_pulmonary), #, " + `Pulmonary Respiratory: `"), 
                                                                     weight_method = "lr")

# models_rsv_15_300$model_weighted_adjusted_time <- run_logistic_regression(df = rsv_iptw_15_300,
#                                                          model_formula = paste0(outcome_15_300,
#                                                                                 formula_no_pulmonary, " + `Pulmonary Respiratory: ` + ce_week_factor"),
#                                                          weight_method = "lr")

var_to_omit <- c("(Intercept)", "util_inpatientno_visits", "util_inpatientlow_utilizer", "util_inpatienthigh_utilizer",
                 "util_inpatientmoderate_utilizer",
                 "util_outpatientno_visits", "util_outpatientlow_utilizer", "util_outpatienthigh_utilizer", "util_outpatientmoderate_utilizer",
                 "util_edno_visits", "util_edlow_utilizer", "util_edhigh_utilizer", "util_edmoderate_utilizer",
                 "util_otherno_visits", "util_otherlow_utilizer", "util_otherhigh_utilizer", "util_othermoderate_utilizer")

p_s4a <- plot_summs(models_rsv_15_300$model_unweighted_unadjusted,
           models_rsv_15_300$model_unweighted_adjusted,
           models_rsv_15_300$model_weighted_unadjusted,
           models_rsv_15_300$model_weighted_adjusted,
           omit.coefs = var_to_omit,
           robust = TRUE,
           # models$model_weighted_adjusted_time,
           model.names = c("Unweighted, unadjusted",
                           "Unweighted, adjusted",
                           "Weighted (LR), unadjusted",
                           "Weighted (LR), adjusted"),
           # "Weighted, adjusted for CE week"),
           exp = TRUE)
p_s4a <- p_s4a + scale_y_discrete(labels = c("Pulmonary Respiratory", 
                                           "Hopspitalized for index infection", 
                                           "Male", 
                                           "Other/Unknown Race", "Non-Hispanic White", "Non-Hispanic Multiple", "Non-Hispanic Black/AA", "Non-Hispanic Asian/PI",
                                           "6m-1y old", "4-5y old", "3-4y old", "2-3y old", "1-2y old", "SARS-CoV-2 Infection")) +
  labs(x = "Odd ratios", y = "") 

ggsave("figures/NEW_Figure_s4a_rsv_15_300.png", plot = p_s4a, width = 20, height = 10, unit = "cm")

```

```{r new_figs4a_stats, results = "asis", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
export_summs(models_rsv_15_300$model_unweighted_unadjusted,
           models_rsv_15_300$model_unweighted_adjusted,
           models_rsv_15_300$model_weighted_unadjusted,
           models_rsv_15_300$model_weighted_adjusted,
             # models$model_weighted_adjusted_time,
             model.names = c("Unweighted, unadjusted",
                             "Unweighted, adjusted",
                             "Weighted (LR), unadjusted",
                             "Weighted (LR), adjusted"),
             # "Weighted, adjusted for CE week"),
             exp = TRUE,
             error_format = "[{conf.low}, {conf.high}]")
```

# Figure S4b: RSV within 30-180 days (past post-acute)

```{r figure_s4b_rsv_30_180, echo = FALSE, output = FALSE, message = FALSE , warning = FALSE}

outcome_30_180 = "outcome_rsv_30_to_180"
comparison_group = "Influenza"

# iptw_flu_15_180 <- analytic_dataset_final %>%
#   mutate(exclude = case_when( is.na(days_from_index_to_rsv) ~ 0,
#                               days_from_index_to_rsv >= 15 ~ 0,
#                               TRUE ~ 1)) %>%
#   filter(exclude==0) %>%
#   do_iptw(cohort_entry_start_date = cohort_entry_start_date,
#           comparison_cohort = comparison_group,
#           weight_formula = "covid~age_group+sex_cat+race_eth_cat+ce_week_factor",
#           iptw_description = paste0("covid_", comparison_group, "_", outcome_15_180))

rsv_iptw_30_180 <- results_tbl( paste0(paste0("covid_", comparison_group, "_", outcome_30_180),'_tabc')) %>%
  collect()

models_rsv_30_180 = list()

models_rsv_30_180$model_unweighted_unadjusted <- run_logistic_regression(df = rsv_iptw_30_180,
                                                       model_formula = paste0(outcome_30_180, " ~ covid"),
                                                       weight_method = "none")

models_rsv_30_180$model_unweighted_adjusted <- run_logistic_regression(df = rsv_iptw_30_180,
                                                         model_formula = paste0(outcome_30_180,
                                                                                formula_no_pulmonary, " + pulmonary_respiratory"), 
                                                         weight_method = "none")

models_rsv_30_180$model_weighted_unadjusted <- run_logistic_regression(df = rsv_iptw_30_180,
                                                       model_formula = paste0(outcome_30_180, " ~ covid"),
                                                       weight_method = "lr")

models_rsv_30_180$model_weighted_adjusted <- run_logistic_regression(df = rsv_iptw_30_180,
                                                         model_formula = paste0(outcome_30_180,
                                                                                formula_no_pulmonary), #" + `Pulmonary Respiratory: `"), 
                                                         weight_method = "lr")

models_rsv_30_180$model_weighted_adjusted_time <- run_logistic_regression(df = rsv_iptw_30_180,
                                                         model_formula = paste0(outcome_30_180,
                                                                                formula_no_pulmonary, " + pulmonary_respiratory + ce_week_factor"),
                                                         weight_method = "lr")

p_s4b <- plot_summs(models_rsv_30_180$model_unweighted_unadjusted,
           models_rsv_30_180$model_unweighted_adjusted,
           models_rsv_30_180$model_weighted_unadjusted,
           models_rsv_30_180$model_weighted_adjusted,
           omit.coefs = var_to_omit,  
           robust = TRUE,  
           # models$model_weighted_adjusted_time,
           model.names = c("Unweighted, unadjusted",
                           "Unweighted, adjusted",
                           "Weighted (LR), unadjusted",
                           "Weighted (LR), adjusted"),
                           # "Weighted, adjusted for CE week"),
           exp = TRUE)
p_s4b <- p_s4b + scale_y_discrete(labels = c("Pulmonary Respiratory", 
                                "Hopspitalized for index infection", 
                                "Male", 
                                "Other/Unknown Race", "Non-Hispanic White", "Non-Hispanic Multiple", "Non-Hispanic Black/AA", "Non-Hispanic Asian/PI",
                                "6m-1y old", "4-5y old", "3-4y old", "2-3y old", "1-2y old", "SARS-CoV-2 Infection")) +
                labs(x = "Odd ratios", y = "") 

ggsave("figures/NEW_Figure_s4b_rsv_30_180.png", plot = p_s4b, width = 20, height = 10, units = "cm")

```

```{r new_figs4b_stats, results = "asis", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
export_summs(models_rsv_30_180$model_unweighted_unadjusted,
           models_rsv_30_180$model_unweighted_adjusted,
           models_rsv_30_180$model_weighted_unadjusted,
           models_rsv_30_180$model_weighted_adjusted,
           # models$model_weighted_adjusted_time,
           model.names = c("Unweighted, unadjusted",
                           "Unweighted, adjusted",
                           "Weighted (LR), unadjusted",
                           "Weighted (LR), adjusted"),
                           # "Weighted, adjusted for CE week"),
           exp = TRUE)
```

# Figure S5a: Sensitivity analysis: Subsequent Respiratory infection within 30-180 days, EXCLUDING COVID
```{r fig_s5a_sub_resp_with_covid_30_180, echo = FALSE, output = FALSE, message = FALSE , warning = FALSE}

outcome_ari = "outcome_resp30d"
comparison_group_ari ="Influenza"

# iptw_flu_2b_no_covid <- analytic_dataset_final_resp %>%
#   filter(resp_outcome_is_reinfection=="0") %>% # TODO allow for re-infection
#   do_iptw(cohort_entry_start_date = cohort_entry_start_date,
#           comparison_cohort = comparison_group,
#           weight_formula = "covid~age_group+sex_cat+race_eth_cat+ce_week_factor+pulmonary_respiratory",
#           iptw_description = paste0("resp_study_covid_", comparison_group, "_", outcome_ari))

dataset_with_iptw_ari <- results_tbl( paste0(paste0("resp_study_covid_", comparison_group_ari, "_", outcome_ari),'_tabc')) %>%
  collect()

models_ari = list()

models_ari$model_unweighted_unadjusted <- run_logistic_regression(df = dataset_with_iptw_ari,
                                                       model_formula = paste0(outcome_ari, " ~ covid"),
                                                       weight_method = "none")

models_ari$model_unweighted_adjusted <- run_logistic_regression(df = dataset_with_iptw_ari,
                                                         model_formula = paste0(outcome_ari,
                                                                                formula_no_pulmonary, " + pulmonary_respiratory"), 
                                                         weight_method = "none")

models_ari$model_weighted_unadjusted <- run_logistic_regression(df = dataset_with_iptw_ari,
                                                       model_formula = paste0(outcome_ari, " ~ covid"),
                                                       weight_method = "lr")

# TODO something is wrong with inpatient
models_ari$model_weighted_adjusted <- run_logistic_regression(df = dataset_with_iptw_ari,
                                                         model_formula = paste0(outcome_ari,
                                                                                formula_no_pulmonary, " + pulmonary_respiratory"), 
                                                         weight_method = "lr")

# models_ari$model_weighted_adjusted_time <- run_logistic_regression(df = dataset_with_iptw_ari,
#                                                          model_formula = paste0(outcome_ari,
#                                                                                 " ~ `SARS-CoV-2 Infection: ` + `Age groups: ` + `Race: ` + `Gender: ` + `Hospitalized for index infection: ` + `Prior inpatient visit frequency: `+ `Prior outpatient visit frequency: ` + `Prior ER visit frequency: ` + `Prior other visit frequency: ` + `Pulmonary Respiratory: ` + ce_week_factor"),
                                                         # weight_method = "lr")

```

```{r figure_5a_exclude_covid, echo = FALSE, warning = FALSE, message = FALSE, fig.width=12, fig.height=6}

p_s5a <- plot_summs(models_ari$model_unweighted_unadjusted,
           models_ari$model_unweighted_adjusted,
           models_ari$model_weighted_unadjusted,
           models_ari$model_weighted_adjusted,
           # models$model_weighted_adjusted_time,
           omit.coefs = var_to_omit,  
           model.names = c("Unweighted, unadjusted",
                           "Unweighted, adjusted",
                           "Weighted (LR), unadjusted",
                           "Weighted (LR), adjusted"),
                           # "Weighted, adjusted for CE week"),
           exp = TRUE)
p_s5a <- p_s5a + scale_y_discrete(labels = c("Pulmonary Respiratory", 
                                "Hopspitalized for index infection", 
                                "Male", 
                                "Other/Unknown Race", "Non-Hispanic White", "Non-Hispanic Multiple", "Non-Hispanic Black/AA", "Non-Hispanic Asian/PI",
                                "6m-1y old", "4-5y old", "3-4y old", "2-3y old", "1-2y old", "SARS-CoV-2 Infection")) +
                labs(x = "Odd ratios", y = "") 

ggsave("figures/NEW_Figure_s5a_ari_exclude_covid_30_180.png", plot = p_s5a, width = 20, height = 10, units = "cm")
```

```{r new_figs5a_stats, results = "asis", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
export_summs(models_ari$model_unweighted_unadjusted,
             models_ari$model_unweighted_adjusted,
             models_ari$model_weighted_unadjusted,
             models_ari$model_weighted_adjusted,
             # models$model_weighted_adjusted_time,
             model.names = c("Unweighted, unadjusted",
                             "Unweighted, adjusted",
                             "Weighted (LR), unadjusted",
                             "Weighted (LR), adjusted"),
                           # "Weighted, adjusted for CE week"),
           exp = TRUE, error_format = "[{conf.low}, {conf.high}]")
```

# Figure S5b: Sensitivity analysis: Subsequent Respiratory infection within 15-180 days, EXCLUDING COVID
```{r sub_resp_with_covid_15_180, echo = FALSE, output = FALSE, message = FALSE , warning = FALSE}

outcome_ari_15 = "outcome_resp15d"
comparison_group_ari = "Influenza"

# iptw_flu_5b_no_covid <- analytic_dataset_final_resp %>%
#   filter(resp_outcome_is_reinfection=="0") %>% # TODO allow for re-infection
#   do_iptw(cohort_entry_start_date = cohort_entry_start_date,
#           comparison_cohort = comparison_group,
#           weight_formula = "covid~age_group+sex_cat+race_eth_cat+ce_week_factor+pulmonary_respiratory",
#           iptw_description = paste0("resp_covid_", comparison_group, "_", outcome_ari_15))

dataset_with_iptw_ari_15 <- results_tbl( paste0(paste0("resp_covid_", comparison_group_ari, "_", outcome_ari_15),'_tabc')) %>%
  collect()

models_ari_15 = list()

models_ari_15$model_unweighted_unadjusted <- run_logistic_regression(df = dataset_with_iptw_ari_15,
                                                       model_formula = paste0(outcome_ari_15, " ~ covid"),
                                                       weight_method = "none")

models_ari_15$model_unweighted_adjusted <- run_logistic_regression(df = dataset_with_iptw_ari_15,
                                                         model_formula = paste0(outcome_ari_15,
                                                                                formula_no_pulmonary, " + pulmonary_respiratory"), 
                                                         weight_method = "none")

models_ari_15$model_weighted_unadjusted <- run_logistic_regression(df = dataset_with_iptw_ari_15,
                                                       model_formula = paste0(outcome_ari_15, " ~ covid"),
                                                       weight_method = "lr")

# TODO something is wrong with inpatient
models_ari_15$model_weighted_adjusted <- run_logistic_regression(df = dataset_with_iptw_ari_15,
                                                         model_formula = paste0(outcome_ari_15,
                                                                                formula_no_pulmonary, " + pulmonary_respiratory"), 
                                                         weight_method = "lr")

# models_ari$model_weighted_adjusted_time <- run_logistic_regression(df = dataset_with_iptw_ari,
#                                                          model_formula = paste0(outcome_ari,
#                                                                                 " ~ `SARS-CoV-2 Infection: ` + `Age groups: ` + `Race: ` + `Gender: ` + `Hospitalized for index infection: ` + `Prior inpatient visit frequency: `+ `Prior outpatient visit frequency: ` + `Prior ER visit frequency: ` + `Prior other visit frequency: ` + `Pulmonary Respiratory: ` + ce_week_factor"),
                                                         # weight_method = "lr")

```

```{r figure_5b_exclude_covid, echo = FALSE, warning = FALSE, message = FALSE, fig.width=12, fig.height=6}

p_s5b <- plot_summs(models_ari_15$model_unweighted_unadjusted,
           models_ari_15$model_unweighted_adjusted,
           models_ari_15$model_weighted_unadjusted,
           models_ari_15$model_weighted_adjusted,
           # models$model_weighted_adjusted_time,
           omit.coefs = var_to_omit,  
           model.names = c("Unweighted, unadjusted",
                           "Unweighted, adjusted",
                           "Weighted (LR), unadjusted",
                           "Weighted (LR), adjusted"),
                           # "Weighted, adjusted for CE week"),
           exp = TRUE)
p_s5b <- p_s5b + scale_y_discrete(labels = c("Pulmonary Respiratory", 
                                "Hopspitalized for index infection", 
                                "Male", 
                                "Other/Unknown Race", "Non-Hispanic White", "Non-Hispanic Multiple", "Non-Hispanic Black/AA", "Non-Hispanic Asian/PI",
                                "6m-1y old", "4-5y old", "3-4y old", "2-3y old", "1-2y old", "SARS-CoV-2 Infection")) +
                labs(x = "Odd ratios", y = "") 

ggsave("figures/NEW_Figure_s5b_ari_exclude_covid_15_180.png", plot = p_s5b, width = 20, height = 10, units = "cm")
```

```{r new_figs5b_stats, results = "asis", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
export_summs(models_ari_15$model_unweighted_unadjusted,
           models_ari_15$model_unweighted_adjusted,
           models_ari_15$model_weighted_unadjusted,
           models_ari_15$model_weighted_adjusted,
             # models$model_weighted_adjusted_time,
             model.names = c("Unweighted, unadjusted",
                             "Unweighted, adjusted",
                             "Weighted (LR), unadjusted",
                             "Weighted (LR), adjusted"),
                           # "Weighted, adjusted for CE week"),
           exp = TRUE, error_format = "[{conf.low}, {conf.high}]")
```

# Figure S5c: Sensitivity analysis: Subsequent General (any) infection within 30-180 days (**excluding covid**)
```{r general_infection_no_covid_30_180, echo = FALSE, output = FALSE, message = FALSE , warning = FALSE}

outcome = "outcome_general30d"
comparison_group = "Influenza"

# iptw_flu_2c_exclude_covid <- analytic_dataset_final_resp %>%
#   filter(resp_outcome_is_reinfection=="0") %>% # TODO allow for re-infection
#   do_iptw(cohort_entry_start_date = cohort_entry_start_date_resp,
#           comparison_cohort = comparison_group_ari,
#           weight_formula = "covid~age_group+sex_cat+race_eth_cat+ce_week_factor+pulmonary_respiratory",
#           iptw_description = paste0("resp_stdy_covid_", comparison_group, "_", outcome))

dataset_with_iptw <- results_tbl( paste0(paste0("resp_stdy_covid_", comparison_group, "_", outcome),'_tabc')) %>%
  collect()

models = list()

models$model_unweighted_unadjusted <- run_logistic_regression(df = dataset_with_iptw,
                                                       model_formula = paste0(outcome, "~ covid"),
                                                       weight_method = "none")

models$model_unweighted_adjusted <- run_logistic_regression(df = dataset_with_iptw,
                                                         model_formula = paste0(outcome,
                                                                               formula_no_pulmonary, " + pulmonary_respiratory"), 
                                                         weight_method = "none")

models$model_weighted_unadjusted <- run_logistic_regression(df = dataset_with_iptw,
                                                       model_formula = paste0(outcome, 
                                                                              " ~ covid"),
                                                       weight_method = "lr")

# TODO something is wrong with inpatient
models$model_weighted_adjusted <- run_logistic_regression(df = dataset_with_iptw,
                                                         model_formula = paste0(outcome,
                                                                                formula_no_pulmonary, " + pulmonary_respiratory"), 
                                                         weight_method = "lr")

# models$model_weighted_adjusted_time <- run_logistic_regression(df = dataset_with_iptw,
#                                                          model_formula = paste0(outcome,
#                                                                                 "~ `SARS-CoV-2 Infection: ` + `Age groups: ` + `Race: ` + `Gender: ` + `Hospitalized for index infection: ` + `Prior inpatient visit frequency: `+ `Prior outpatient visit frequency: ` + `Prior ER visit frequency: ` + `Prior other visit frequency: ` + `Pulmonary Respiratory: ` + ce_week_factor"),
#                                                          weight_method = "lr")

```

```{r figure_s5c_no_covid, echo = FALSE, warning = FALSE, message = FALSE, fig.width=12, fig.height=6}

p_s5c <- plot_summs(models$model_unweighted_unadjusted,
           models$model_unweighted_adjusted,
           models$model_weighted_unadjusted,
           models$model_weighted_adjusted,
           omit.coefs = var_to_omit,  
           # models$model_weighted_adjusted_time,
           model.names = c("Unweighted, unadjusted",
                           "Unweighted, adjusted",
                           "Weighted (LR), unadjusted",
                           "Weighted (LR), adjusted"),
                           # "Weighted, adjusted for CE week"),
           exp = TRUE)

p_s5c <- p_s5c + scale_y_discrete(labels = c("Pulmonary Respiratory", 
                                "Hopspitalized for index infection", 
                                "Male", 
                                "Other/Unknown Race", "Non-Hispanic White", "Non-Hispanic Multiple", "Non-Hispanic Black/AA", "Non-Hispanic Asian/PI",
                                "6m-1y old", "4-5y old", "3-4y old", "2-3y old", "1-2y old", "SARS-CoV-2 Infection")) +
                labs(x = "Odd ratios", y = "") 

ggsave("figures/NEW_Figure_s5c_general_exclude_covid_30_180.png", plot = p_s5c, width = 20, height = 10, units = "cm")
```

```{r new_figs5c_stats, results = "asis", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
export_summs(models$model_unweighted_unadjusted,
           models$model_unweighted_adjusted,
           models$model_weighted_unadjusted,
           models$model_weighted_adjusted,
           # models$model_weighted_adjusted_time,
           model.names = c("Unweighted, unadjusted",
                           "Unweighted, adjusted",
                           "Weighted (LR), unadjusted",
                           "Weighted (LR), adjusted"),
                           # "Weighted, adjusted for CE week"),
           exp = TRUE, error_format = "[{conf.low}, {conf.high}]")
```

# Figure S5d: Sensitivity analysis: Subsequent General (any) infection within 15-180 days (**including covid**)
```{r general_infection_with_covid_15_180, echo = FALSE, output = FALSE, message = FALSE , warning = FALSE}

# TODO really need to figure out what the deal with utilization is
# Of I know why

outcome_general_15_180 = "outcome_general15d"
comparison_group = "Influenza"

# any_inf_iptw_flu_outcome_general_15_180 <- analytic_dataset_final_resp %>%
#   filter(resp_outcome_is_reinfection=="0") %>% # TODO allow for re-infection
#   do_iptw(cohort_entry_start_date = cohort_entry_start_date_resp,
#           comparison_cohort = comparison_group,
#           weight_formula = "covid~age_group+sex_cat+race_eth_cat+ce_week_factor+pulmonary_respiratory",
#           iptw_description = paste0("resp_study_covid_", comparison_group, "_", outcome_general_15_180))

dataset_with_iptw_general_15_180 <- results_tbl( paste0(paste0("resp_covid_", comparison_group, "_", outcome_general_15_180),'_tabc')) %>%
  collect()

models_general_15_180 = list()

models_general_15_180$model_unweighted_unadjusted <- run_logistic_regression(df = dataset_with_iptw_general_15_180,
                                                       model_formula = paste0(outcome_general_15_180, " ~ covid"),
                                                       weight_method = "none")

models_general_15_180$model_unweighted_adjusted <- run_logistic_regression(df = dataset_with_iptw_general_15_180,
                                                         model_formula = paste0(outcome_general_15_180,
                                                                                formula_no_pulmonary, " + pulmonary_respiratory"), 
                                                         weight_method = "none")

models_general_15_180$model_weighted_unadjusted <- run_logistic_regression(df = dataset_with_iptw_general_15_180,
                                                       model_formula = paste0(outcome_general_15_180, " ~ covid"),
                                                       weight_method = "lr")

# TODO something is wrong with inpatient
models_general_15_180$model_weighted_adjusted <- run_logistic_regression(df = dataset_with_iptw_general_15_180,
                                                         model_formula = paste0(outcome_general_15_180,
                                                                               formula_no_pulmonary, " + pulmonary_respiratory"), 
                                                         weight_method = "lr")

# models$model_weighted_adjusted_time <- run_logistic_regression(df = dataset_with_iptw,
#                                                          model_formula = paste0(outcome,
#                                                                                 " ~ `SARS-CoV-2 Infection: ` + `Age groups: ` + `Race: ` + `Gender: ` + `Hospitalized for index infection: ` + `Prior inpatient visit frequency: `+ `Prior outpatient visit frequency: ` + `Prior ER visit frequency: ` + `Prior other visit frequency: ` + `Pulmonary Respiratory: ` + ce_week_factor"),
#                                                          weight_method = "lr")

```

```{r figure_s5d, echo = FALSE, warning = FALSE, message = FALSE, fig.width=12, fig.height=6}

p_s5d <- plot_summs(models_general_15_180$model_unweighted_unadjusted,
           models_general_15_180$model_unweighted_adjusted,
           models_general_15_180$model_weighted_unadjusted,
           models_general_15_180$model_weighted_adjusted,
           omit.coefs = var_to_omit,  
           # models$model_weighted_adjusted_time,
           model.names = c("Unweighted, unadjusted",
                           "Unweighted, adjusted",
                           "Weighted (LR), unadjusted",
                           "Weighted (LR), adjusted"),
                           # "Weighted, adjusted for CE week"),
           exp = TRUE)
p_s5d <- p_s5d + scale_y_discrete(labels = c("Pulmonary Respiratory", 
                                "Hopspitalized for index infection", 
                                "Male", 
                                "Other/Unknown Race", "Non-Hispanic White", "Non-Hispanic Multiple", "Non-Hispanic Black/AA", "Non-Hispanic Asian/PI",
                                "6m-1y old", "4-5y old", "3-4y old", "2-3y old", "1-2y old", "SARS-CoV-2 Infection")) +
                labs(x = "Odd ratios", y = "") 

ggsave("figures/NEW_Figure_s5d_general_exclude_covid_15_180.png", plot = p_s5c, width = 20, height = 10, units = "cm")
```

```{r new_figs5d_stats, results = "asis", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
export_summs(models_general_15_180$model_unweighted_unadjusted,
           models_general_15_180$model_unweighted_adjusted,
           models_general_15_180$model_weighted_unadjusted,
           models_general_15_180$model_weighted_adjusted,
           # models$model_weighted_adjusted_time,
           model.names = c("Unweighted, unadjusted",
                           "Unweighted, adjusted",
                           "Weighted (LR), unadjusted",
                           "Weighted (LR), adjusted"),
                           # "Weighted, adjusted for CE week"),
           exp = TRUE, error_format = "[{conf.low}, {conf.high}]")
```

